A New Method of Modelling Tuneable Lasers with Functional Composition

### 2019-11-13 Papers/Journal/Tuneable_Lasers.tex
Partially fixed plot

set xtics ('Loss' 2, 'Disp.' 6, 'Mod.' 10, 'Gain' 14)

@@

set view 45,325,1.25
set pm3d
set pm3d interpolate 5,5

#set contour surface
unset cl
unset colorbox

sp '../../Evolution.dat' u 2:1:3 w l lw 0.3 lc 8 not
\end{gnuplot}
\caption{}
\label{fig:}
\end{figure*}

>>>>

set xtics ('Loss' 3, 'Disp.' 9, 'Mod.' 15, 'Gain' 21)

@@

set view 45,325,1.25

unset colorbox

set samples 10

sp '../../EBig.dat' u ($2*0.1):1:3 w pm3d not, \
'../../Evolution.dat' u 2:1:3 w l lw 0.3 lc 8 not
\end{gnuplot}
\caption{}
\label{fig:}
\end{figure*}
